Perfect Queries for Non-interactive\\Ulam Searching Game with Many Lies

### 2018-05-05 src/tex/paper.tex
coba bikin curhatan genrator matrix

@@

\section{Generate query with generator matrix}

An $(n,M,d)_2$ binary code can be generated by using linear combination of a generator matrix $G$ where $G$ is a $n \times m$ matrix and $2^m = M$. Generator matrix $[7,3,4]2$ in Figure \ref{fig:generator734} can create a perfect binary code $(7,8,4)_2$ code in Figure \ref{fig:binarycode784}.

A generator matrix $[n, m]2$ where $n = 2^m - 1$ and each column is a linear combination of $m$ bit binary string except $\vec{0}$ can make a perfect binary code $(n,M,d)_2$ where $d = M/2$. \textbf{\textit{We need a profing :(}}

\begin{figure}
\centering
\begin{BVerbatim}
1001101
0101011
0010111
\end{BVerbatim}
\caption{Generator matrix $[7,3]_2$}
\label{fig:generator734}
\end{figure}

Assume that $g_i$ is row of $G$. Then we iterate each $g_i$ to make new query until Hamming distance reaches what we need. If we need more than $M/2$ Hamming distance, repeat.

>>>>

\section{Generate binary code with generator matrix}

An $(n,M,d)_2$ binary code can be generated by using linear combination of each row of a generator matrix $[n,m,d]_2$ where $2^m = M$. A Generator matrix $G$ is an $n \times m$ matrix. Now see that binary code $(6,8,3)_2$ in Figure \ref{fig:binarycode683} can be generated using generator matrix $[6,3,3]_2$ in Figure \ref{fig:generator633}. Assume that each row of $[6,3,3]_2$ is $g_1$, $g_2$, and $g_3$, then binary code $(6,8,3)_2$ is the linear combination of all vectors of the form ${\lambda}_1 g_1 + {\lambda}_2 g_2 + {\lambda}_3 g_3$ where $\lambda{_i} \in \mathbb{F}_2^6$.

Now again see a generator matrix $[7,3,4]_2$ in Figure \ref{fig:generator734} can create a perfect binary code $(7,8,4)_2$ code in Figure \ref{fig:binarycode784}. A generator matrix $[n, m, d]_2$ where $n = 2^m - 1$ and each \textbf{column} is a linear combination of $m$ bit binary string except $\vec{0}$ can make a perfect binary code $(n,M,d)_2$ where $d = M/2$. \textbf{\textit{We need a profing or citation..}}

\begin{figure}
\centering
\begin{BVerbatim}
100110
010101
001011
\end{BVerbatim}
\caption{Generator matrix $[6,3,3]_2$}
\label{fig:generator633}
\end{figure}

\begin{figure}
\centering
\begin{BVerbatim}
1001101
0101011
0010111
\end{BVerbatim}
\caption{Generator matrix $[7,3,4]_2$}
\label{fig:generator734}
\end{figure}

Nah masalahnya, jika $d$ yang kita butuhkan kurang dari $M/2$, maka kita harus menggunakan seminimal mungkin $n$ kolom pertama $[M-1,M,M/2]_2$ sehingga menghasilkan $[n,M,d]_2$. Asumsikan kita memiliki fungsi $\aleph(d)$ adalah berapa kolom pada generator matrix yang akan menghasilkan kode biner dengan minimal jarak Hamming $d$. Hal yang pasti adalah $\aleph(M/2) = M-1$ dan $\aleph(1) = {log}_2(m)$ (need proving). Worst case adalah $\aleph(d)=M/2 + d - 1$. Best case adalah karena ada $M-1$ kolom untuk $0 \leq d \leq M/2$, maka $\aleph(d) = d/2$ (sepertinya tidak mungkin). Nah problem kita adalah bagaimana mengurutkan kolom pada generator matrix sehingga $\aleph(d)$ sesempurna mungkin, atau bisa dikatakan $\aleph(d) - \aleph(d-1) \approx 2$.

% Assume that $g_i$ is row of $G$. Then we iterate each $g_i$ to make new query until Hamming distance reaches what we need. If we need more than $M/2$ Hamming distance, repeat.

@@
